Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-10 paper.qmd
Saved models for Gau

## Set the maximum difference as the criteria
distance_df_small_edges <- distance_gau1 |>
  dplyr::filter(distance < 0.1) |>
  mutate(ID = row_number()) |>
  filter(!(ID %in% c(150, 110))) |>
  dplyr::select(-ID) #benchmark_gau1
```

@@

scaled_gau_data_model <- scaled_gau |>
  filter(type == "model") |>
  select(-type)
```

@@

## Set the maximum difference as the criteria
distance_df_small_edges <- distance_gau1 |>
  dplyr::filter(distance < 0.06) #benchmark_gau1 #benchmark_gau1
```

>>>>

## Set the maximum difference as the criteria
distance_df_small_edges <- distance_gau1 |>
  dplyr::filter(distance < 0.1) |>
  mutate(ID = row_number()) |>
  filter(!(ID %in% c(150, 110))) |>
  dplyr::select(-ID) #benchmark_gau1

# write_rds(distance_df_small_edges, "data/five_gau_clusters/tsne_model.rds")
```

@@

# write_rds(distance_df_small_edges, "data/five_gau_clusters/umap_model.rds")
```

@@

## Set the maximum difference as the criteria
distance_df_small_edges <- distance_gau1 |>
  dplyr::filter(distance < 0.06) #benchmark_gau1 #benchmark_gau1

# write_rds(distance_df_small_edges, "data/five_gau_clusters/pacmap_model.rds")
```
